Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-07 Draft/Draft.Rmd
update percentage of robust interactions

Following Simmons et al. [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs. Prior to analyses, we selected only robust links, that is, interactions whose frequency was greater than one (64.94 % interactions); and, then, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.

>>>>

Following Simmons et al. [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs. Prior to analyses, we selected only robust links, that is, interactions whose frequency was greater than one (64.98 % interactions); and, then, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
